cardinalR: Generating Interesting High-Dimensional Data Structures

### 2025-11-28 paper-cardinalR.Rmd
Added code for table functions

```{r}
branch_tb <- tibble(fun = c("gen_expbranches",
                             "gen_linearbranches",
                             "gen_curvybranches", 
                             "gen_orglinearbranches", 
                             "gen_orgcurvybranches"), 
                      exp = c("Exponential shaped branches.",
                               "Linear shaped branches.", 
                               "Curvy shaped branches.",
                               "Linear shaped branches originated in one point.",
                               "Curvy shaped branches originated in one point."))
```

```{r branching-tb-html, eval=knitr::is_html_output()}
branch_tb |> 
  kable(caption = "cardinalR branching data generation functions", col.names = c("Function", "Explanation"), table.pos = "!ht") 
```

```{r branching-tb-pdf, eval=knitr::is_latex_output()}
branch_tb |> 
  kable(caption = "cardinalR branching data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, table.pos = "!ht")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r arg-branching-tb-html, eval=knitr::is_html_output()}
arg_branching_tb |> 
  kable(caption = "The main arguments for branching shape generators.", col.names = c("Argument", "Type", "Explanation"), table.pos = "!ht") 
```

```{r arg-branching-tb-pdf, eval=knitr::is_latex_output()}
arg_branching_tb |> 
  kable(caption = "The main arguments for branching shape generators.", format="latex", col.names = c("Argument", "Type", "Explanation"), booktabs = T, table.pos = "!ht")  |>
  column_spec(1, width = "1cm") |>
  column_spec(1, width = "2cm") |>
  column_spec(2, width = "3cm")
```

@@

```{r}
cube_tb <- tibble(fun = c("gen_gridcube",
                          "gen_unifcube"), 
                      exp = c("Cube with specified grid points along each axes.",
                              "Cube with uniform points."))
```

```{r cube-tb-html, eval=knitr::is_html_output()}
cube_tb |> 
  kable(caption = "cardinalR cube data generation functions", col.names = c("Function", "Explanation"), table.pos = "!ht") 
```

```{r cube-tb-pdf, eval=knitr::is_latex_output()}
cube_tb |> 
  kable(caption = "cardinalR cube data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, table.pos = "!ht")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r}
polynomial_tb <- tibble(fun = c("gen_quadratic",
                                "gen_cubic"), 
                        exp = c("Quadratic pattern.",
                                "Cubic pattern."))
```

```{r polynomial-tb-html, eval=knitr::is_html_output()}
polynomial_tb |> 
  kable(caption = "cardinalR polynomial data generation functions", col.names = c("Function", "Explanation"), table.pos = "!ht") 
```

```{r polynomial-tb-pdf, eval=knitr::is_latex_output()}
polynomial_tb |> 
  kable(caption = "cardinalR polynomial data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, table.pos = "!ht")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r}
pyramid_tb <- tibble(fun = c("gen_pyrrect",
                             "gen_pyrtri",
                             "gen_pyrstar",
                             "gen_pyrfrac"), 
                        exp = c("Rectangular-base, with a sharp or blunted apex.",
          "Triangular-base, with a sharp or blunted apex.",
          "Star-shaped base, with a sharp or blunted apex.",
          "Pyramid with triangular pyramid-shaped holes."))
```

```{r pyramid-tb-html, eval=knitr::is_html_output()}
pyramid_tb |> 
  kable(caption = "cardinalR pyramid data generation functions", col.names = c("Function", "Explanation"), table.pos = "!ht") 
```

```{r pyramid-tb-pdf, eval=knitr::is_latex_output()}
pyramid_tb |> 
  kable(caption = "cardinalR pyramid data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, table.pos = "!ht")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r}
sphere_tb <- tibble(fun = c("gen_circle",
                            "gen_curvycycle",
                            "gen_unifsphere",
                            "gen_hollowsphere",
                            "gen_gridedsphere",
                            "gen_clusteredspheres",
                            "gen_hemisphere"), 
                        exp = c("Circle.",
                                "Curvy cell cycle.",
                                "Uniform ball.",
                                "Hollow sphere.",
                                "Grided sphere.",
                                "Multiple small spheres within a big sphere.",
                                "Hemisphere."))
```

```{r sphere-tb-html, eval=knitr::is_html_output()}
sphere_tb |> 
  kable(caption = "cardinalR sphere data generation functions", col.names = c("Function", "Explanation"), linesep = "", table.pos = "!ht") 
```

```{r sphere-tb-pdf, eval=knitr::is_latex_output()}
sphere_tb |> 
  kable(caption = "cardinalR sphere data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, linesep = "", table.pos = "!ht")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r}
trefoil_tb <- tibble(fun = c("gen_trefoil4d",
                            "gen_trefoil3d"), 
                        exp = c("Trefoil in 4-D.",
                                "Trefoil in 3-D."))
```

```{r trefoil-tb-html, eval=knitr::is_html_output()}
trefoil_tb |> 
  kable(caption = "cardinalR trefoil data generation functions", col.names = c("Function", "Explanation"), table.pos = "!ht") 
```

@@

trefoil_tb |> 
  kable(caption = "cardinalR trefoil data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, table.pos = "!ht")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r}
trigonometric_tb <- tibble(fun = c("gen_crescent",
                            "gen_curvycylinder",
                            "gen_sphericalspiral",
                            "gen_helicalspiral",
                            "gen_conicspiral",
                            "gen_nonlinear"), 
                        exp = c("Crescent pattern.",
                                "Curvy cylinder.",
                                "Spherical spiral.",
                                "Helical spiral.",
                                "Conic spiral.",
                                "Nonlinear hyperbola."))
```

```{r trigonometric-tb-html, eval=knitr::is_html_output()}
trigonometric_tb |> 
  kable(caption = "cardinalR trigonometric data generation functions", col.names = c("Function", "Explanation"), linesep = "", table.pos = "!ht") 
```

```{r trigonometric-tb-pdf, eval=knitr::is_latex_output()}
trigonometric_tb |> 
  kable(caption = "cardinalR trigonometric data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, linesep = "", table.pos = "!ht")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r}
noise_fun_tb <- tibble(fun = c("gen_noisedims",
                            "gen_wavydims1",
                            "gen_wavydims2",
                            "gen_wavydims3"), 
                        exp = c("Gaussian noise dimensions with optional mean and standard deviation.",
                                "Wavy noise dimensions based on a user-specified theta sequence with added jitter.",
                                "Wavy noise dimensions using polynomial transformations of an existing dimension vector.",
                                "Wavy noise dimensions using a combination of polynomial and sine transformations based on the first three dimensions of a dataset."))
```

```{r noise-tb-html, eval=knitr::is_html_output()}
noise_fun_tb |> 
  kable(caption = "cardinalR noise dimensions generation functions", col.names = c("Function", "Explanation"), table.pos = "!ht") 
```

```{r noise-tb-pdf, eval=knitr::is_latex_output()}
noise_fun_tb |> 
  kable(caption = "cardinalR noise dimensions generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, table.pos = "!ht")  |>
  column_spec(1, width = "2.5cm") |>
  column_spec(2, width = "10.5cm")
```

@@

```{r}
odd_shapes_tb <- tibble(fun = c("make_mobiusgau",
                                "make_multigau",
                                "make_curvygau",
                                "make_klink_circles",
                                "make_chain_circles",
                                "make_klink_curvycycle",
                                "make_chain_curvycycle",
                                "make_gaucircles",
                                "make_gaucurvycycle",
                                "make_onegrid",
                                "make_twogrid_overlap",
                                "make_twogrid_shift",
                                "make_shape_para",
                                "make_three_clust_"), 
                        exp = c(
    "Möbius-like cluster combined with a Gaussian.",
    "Multiple Gaussian clusters in high-dimensional space.",
    "Curvilinear cluster with a Gaussian cluster.",
    "K-link circular clusters (non-linear circular patterns).",
    "Chain-like circular clusters connected sequentially.",
    "K-link curvy cycle clusters (curvilinear loop structures).",
    "Chain-like curvy cycle clusters connected sequentially.",
    "Circular clusters with a Gaussian cluster in the middle.",
    "Curvy circular clusters with a Gaussian in the middle.",
    "Single grid in two dimensions.",
    "Two overlapping grids.",
    "Two grids shifted relative to each other.",
    "Parallel shaped clusters.",
    "Three clusters with different shapes. (eg:- 01, 02, ..., 20)"))
```

```{r odd-shape-tb-html, eval=knitr::is_html_output()}
odd_shapes_tb |> 
  kable(caption = "cardinalR multiple clusters generation functions", col.names = c("Function", "Explanation"), linesep = "", table.pos = "!ht") 
```

```{r odd-shape-tb-pdf, eval=knitr::is_latex_output()}
odd_shapes_tb |> 
  kable(caption = "cardinalR multiple clusters generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, linesep = "", table.pos = "!ht")  |>
  column_spec(1, width = "3.5cm") |>
  column_spec(2, width = "8.5cm")
```

@@

```{r}
add_fun_tb <- tibble(fun = c("gen_bkgnoise",
                            "randomize_rows",
                            "relocate_clusters",
                            "gen_nproduct",
                            "gen_nsum",
                            "normalize_data"), 
                        exp = c("Adds background noise.",
                                "Randomizes the rows of input data.",
                                "Relocates the clusters.",
                                "Generates a vector of positive integers whose product is approximately equal to a target value.",
                                "Generates a vector of positive integers whose summation is approximately equal to a target value.", 
                                "Normalizes data."))
```

```{r add-tb-html, eval=knitr::is_html_output()}
add_fun_tb |> 
  kable(caption = "cardinalR additional functions", col.names = c("Function", "Explanation"), linesep = "", table.pos = "!ht") 
```

```{r add-tb-pdf, eval=knitr::is_latex_output()}
add_fun_tb |> 
  kable(caption = "cardinalR additional functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, linesep = "", table.pos = "!ht")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

>>>>

```{r}
branch_tb <- tibble(fun = c("gen_expbranches",
                             "gen_linearbranches",
                             "gen_curvybranches", 
                             "gen_orglinearbranches", 
                             "gen_orgcurvybranches"), 
                      exp = c("Exponential shaped branches.",
                               "Linear shaped branches.", 
                               "Curvy shaped branches.",
                               "Linear shaped branches originated in one point.",
                               "Curvy shaped branches originated in one point.")) |> 
   mutate(fun = gsub("_", "\\\\_", fun))
```

```{r branching-tb-html, eval=knitr::is_html_output()}
branch_tb |> 
  mutate(fun = paste0("<code>", fun, "</code>")) |> 
  kable(caption = "cardinalR branching data generation functions", col.names = c("Function", "Explanation"), escape = FALSE, table.pos = "!ht") 
```

```{r branching-tb-pdf, eval=knitr::is_latex_output()}
branch_tb |>
  mutate(fun = paste0("\\texttt{", fun, "}")) |> 
  kable(caption = "cardinalR branching data generation functions", format="latex", col.names = c("Function", "Explanation"), escape = FALSE, booktabs = T, table.pos = "!ht")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r arg-branching-tb-html, eval=knitr::is_html_output()}
arg_branching_tb |> 
  kable(caption = "The main arguments for branching shape generators.", col.names = c("Argument", "Type", "Explanation"), escape = FALSE, table.pos = "!ht") 
```

```{r arg-branching-tb-pdf, eval=knitr::is_latex_output()}
arg_branching_tb |> 
  kable(caption = "The main arguments for branching shape generators.", format="latex", col.names = c("Argument", "Type", "Explanation"), booktabs = T, escape = FALSE, table.pos = "!ht")  |>
  column_spec(1, width = "1cm") |>
  column_spec(1, width = "2cm") |>
  column_spec(2, width = "3cm")
```

@@

```{r}
cube_tb <- tibble(fun = c("gen_gridcube",
                          "gen_unifcube"), 
                      exp = c("Cube with specified grid points along each axes.",
                              "Cube with uniform points.")) |> 
  mutate(fun = gsub("_", "\\\\_", fun))
```

```{r cube-tb-html, eval=knitr::is_html_output()}
cube_tb |> 
  mutate(fun = paste0("<code>", fun, "</code>")) |>
  kable(caption = "cardinalR cube data generation functions", col.names = c("Function", "Explanation"), escape = FALSE, table.pos = "!ht") 
```

```{r cube-tb-pdf, eval=knitr::is_latex_output()}
cube_tb |> 
  mutate(fun = paste0("\\texttt{", fun, "}")) |>
  kable(caption = "cardinalR cube data generation functions", format="latex", col.names = c("Function", "Explanation"), escape = FALSE, booktabs = T, table.pos = "!ht")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r}
polynomial_tb <- tibble(fun = c("gen_quadratic",
                                "gen_cubic"), 
                        exp = c("Quadratic pattern.",
                                "Cubic pattern.")) |> 
  mutate(fun = gsub("_", "\\\\_", fun))
```

```{r polynomial-tb-html, eval=knitr::is_html_output()}
polynomial_tb |> 
  mutate(fun = paste0("<code>", fun, "</code>")) |> 
  kable(caption = "cardinalR polynomial data generation functions", col.names = c("Function", "Explanation"), escape = FALSE, table.pos = "!ht") 
```

```{r polynomial-tb-pdf, eval=knitr::is_latex_output()}
polynomial_tb |> 
  mutate(fun = paste0("\\texttt{", fun, "}")) |> 
  kable(caption = "cardinalR polynomial data generation functions", format="latex", col.names = c("Function", "Explanation"), escape = FALSE, booktabs = T, table.pos = "!ht")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r}
pyramid_tb <- tibble(fun = c("gen_pyrrect",
                             "gen_pyrtri",
                             "gen_pyrstar",
                             "gen_pyrfrac"), 
                        exp = c("Rectangular-base, with a sharp or blunted apex.",
          "Triangular-base, with a sharp or blunted apex.",
          "Star-shaped base, with a sharp or blunted apex.",
          "Pyramid with triangular pyramid-shaped holes.")) |> 
  mutate(fun = gsub("_", "\\\\_", fun))
```

```{r pyramid-tb-html, eval=knitr::is_html_output()}
pyramid_tb |> 
  mutate(fun = paste0("<code>", fun, "</code>")) |> 
  kable(caption = "cardinalR pyramid data generation functions", col.names = c("Function", "Explanation"), escape = FALSE, table.pos = "!ht") 
```

```{r pyramid-tb-pdf, eval=knitr::is_latex_output()}
pyramid_tb |> 
  mutate(fun = paste0("\\texttt{", fun, "}")) |> 
  kable(caption = "cardinalR pyramid data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, escape = FALSE, table.pos = "!ht")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r}
sphere_tb <- tibble(fun = c("gen_circle",
                            "gen_curvycycle",
                            "gen_unifsphere",
                            "gen_hollowsphere",
                            "gen_gridedsphere",
                            "gen_clusteredspheres",
                            "gen_hemisphere"), 
                        exp = c("Circle.",
                                "Curvy cell cycle.",
                                "Uniform ball.",
                                "Hollow sphere.",
                                "Grided sphere.",
                                "Multiple small spheres within a big sphere.",
                                "Hemisphere.")) |> 
  mutate(fun = gsub("_", "\\\\_", fun))
```

```{r sphere-tb-html, eval=knitr::is_html_output()}
sphere_tb |> 
  mutate(fun = paste0("<code>", fun, "</code>")) |> 
  kable(caption = "cardinalR sphere data generation functions", col.names = c("Function", "Explanation"), linesep = "", escape = FALSE, table.pos = "!ht") 
```

```{r sphere-tb-pdf, eval=knitr::is_latex_output()}
sphere_tb |> 
  mutate(fun = paste0("\\texttt{", fun, "}")) |> 
  kable(caption = "cardinalR sphere data generation functions", format="latex", col.names = c("Function", "Explanation"), escape = FALSE, booktabs = T, linesep = "", table.pos = "!ht")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r}
trefoil_tb <- tibble(fun = c("gen_trefoil4d",
                            "gen_trefoil3d"), 
                        exp = c("Trefoil in 4-D.",
                                "Trefoil in 3-D.")) |> 
  mutate(fun = gsub("_", "\\\\_", fun))
```

```{r trefoil-tb-html, eval=knitr::is_html_output()}
trefoil_tb |> 
  mutate(fun = paste0("<code>", fun, "</code>")) |> 
  kable(caption = "cardinalR trefoil data generation functions", col.names = c("Function", "Explanation"), escape = FALSE, table.pos = "!ht") 
```

@@

trefoil_tb |>
  mutate(fun = paste0("\\texttt{", fun, "}")) |> 
  kable(caption = "cardinalR trefoil data generation functions", format="latex", col.names = c("Function", "Explanation"), escape = FALSE, booktabs = T, table.pos = "!ht")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r}
trigonometric_tb <- tibble(fun = c("gen_crescent",
                            "gen_curvycylinder",
                            "gen_sphericalspiral",
                            "gen_helicalspiral",
                            "gen_conicspiral",
                            "gen_nonlinear"), 
                        exp = c("Crescent pattern.",
                                "Curvy cylinder.",
                                "Spherical spiral.",
                                "Helical spiral.",
                                "Conic spiral.",
                                "Nonlinear hyperbola.")) |> 
  mutate(fun = gsub("_", "\\\\_", fun))
```

```{r trigonometric-tb-html, eval=knitr::is_html_output()}
trigonometric_tb |> 
  mutate(fun = paste0("<code>", fun, "</code>")) |> 
  kable(caption = "cardinalR trigonometric data generation functions", col.names = c("Function", "Explanation"), linesep = "", escape = FALSE, table.pos = "!ht") 
```

```{r trigonometric-tb-pdf, eval=knitr::is_latex_output()}
trigonometric_tb |> 
  mutate(fun = paste0("\\texttt{", fun, "}")) |> 
  kable(caption = "cardinalR trigonometric data generation functions", format="latex", col.names = c("Function", "Explanation"), escape = FALSE, booktabs = T, linesep = "", table.pos = "!ht")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

@@

```{r}
noise_fun_tb <- tibble(fun = c("gen_noisedims",
                            "gen_wavydims1",
                            "gen_wavydims2",
                            "gen_wavydims3"), 
                        exp = c("Gaussian noise dimensions with optional mean and standard deviation.",
                                "Wavy noise dimensions based on a user-specified theta sequence with added jitter.",
                                "Wavy noise dimensions using polynomial transformations of an existing dimension vector.",
                                "Wavy noise dimensions using a combination of polynomial and sine transformations based on the first three dimensions of a dataset.")) |> 
  mutate(fun = gsub("_", "\\\\_", fun))
```

```{r noise-tb-html, eval=knitr::is_html_output()}
noise_fun_tb |> 
  mutate(fun = paste0("<code>", fun, "</code>")) |> 
  kable(caption = "cardinalR noise dimensions generation functions", col.names = c("Function", "Explanation"), escape = FALSE, table.pos = "!ht") 
```

```{r noise-tb-pdf, eval=knitr::is_latex_output()}
noise_fun_tb |> 
  mutate(fun = paste0("\\texttt{", fun, "}")) |> 
  kable(caption = "cardinalR noise dimensions generation functions", format="latex", col.names = c("Function", "Explanation"), escape = FALSE, booktabs = T, table.pos = "!ht")  |>
  column_spec(1, width = "2.5cm") |>
  column_spec(2, width = "10.5cm")
```

@@

```{r}
odd_shapes_tb <- tibble(fun = c("make_mobiusgau",
                                "make_multigau",
                                "make_curvygau",
                                "make_klink_circles",
                                "make_chain_circles",
                                "make_klink_curvycycle",
                                "make_chain_curvycycle",
                                "make_gaucircles",
                                "make_gaucurvycycle",
                                "make_onegrid",
                                "make_twogrid_overlap",
                                "make_twogrid_shift",
                                "make_shape_para",
                                "make_three_clust_"), 
                        exp = c(
    "Möbius-like cluster combined with a Gaussian.",
    "Multiple Gaussian clusters in high-dimensional space.",
    "Curvilinear cluster with a Gaussian cluster.",
    "K-link circular clusters (non-linear circular patterns).",
    "Chain-like circular clusters connected sequentially.",
    "K-link curvy cycle clusters (curvilinear loop structures).",
    "Chain-like curvy cycle clusters connected sequentially.",
    "Circular clusters with a Gaussian cluster in the middle.",
    "Curvy circular clusters with a Gaussian in the middle.",
    "Single grid in two dimensions.",
    "Two overlapping grids.",
    "Two grids shifted relative to each other.",
    "Parallel shaped clusters.",
    "Three clusters with different shapes. (eg:- 01, 02, ..., 20)")) |> 
  mutate(fun = gsub("_", "\\\\_", fun))
```

```{r odd-shape-tb-html, eval=knitr::is_html_output()}
odd_shapes_tb |> 
  mutate(fun = paste0("<code>", fun, "</code>")) |> 
  kable(caption = "cardinalR multiple clusters generation functions", col.names = c("Function", "Explanation"), linesep = "", escape = FALSE, table.pos = "!ht") 
```

```{r odd-shape-tb-pdf, eval=knitr::is_latex_output()}
odd_shapes_tb |> 
  mutate(fun = paste0("\\texttt{", fun, "}")) |> 
  kable(caption = "cardinalR multiple clusters generation functions", format="latex", col.names = c("Function", "Explanation"), escape = FALSE, booktabs = T, linesep = "", table.pos = "!ht")  |>
  column_spec(1, width = "3.5cm") |>
  column_spec(2, width = "8.5cm")
```

@@

```{r}
add_fun_tb <- tibble(fun = c("gen_bkgnoise",
                            "randomize_rows",
                            "relocate_clusters",
                            "gen_nproduct",
                            "gen_nsum",
                            "normalize_data"), 
                        exp = c("Adds background noise.",
                                "Randomizes the rows of input data.",
                                "Relocates the clusters.",
                                "Generates a vector of positive integers whose product is approximately equal to a target value.",
                                "Generates a vector of positive integers whose summation is approximately equal to a target value.", 
                                "Normalizes data.")) |> 
  mutate(fun = gsub("_", "\\\\_", fun))
```

```{r add-tb-html, eval=knitr::is_html_output()}
add_fun_tb |> 
  mutate(fun = paste0("<code>", fun, "</code>")) |> 
  kable(caption = "cardinalR additional functions", col.names = c("Function", "Explanation"), linesep = "", escape = FALSE, table.pos = "!ht") 
```

```{r add-tb-pdf, eval=knitr::is_latex_output()}
add_fun_tb |> 
  mutate(fun = paste0("\\texttt{", fun, "}")) |> 
  kable(caption = "cardinalR additional functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, linesep = "", escape = FALSE, table.pos = "!ht")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```
